Standalone Tactics using OpenTheory

### 2012-02-11 paper.tex
some sentences for sec 4

System on TPTP~\cite{DBLP:conf/lpar/Sutcliffe10}.
<Comparison to THF?>
Evidential tool bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb}.
Omega.
MathServe?
Natural extension of the integration of automatic tools into interactive systems.

>>>>

An impressive example of providing reasoning infrastructure over the web is the System on TPTP~\cite{DBLP:conf/lpar/Sutcliffe10}.
Here, multiple automatic theorem provers can be called on a problem (\eg satisfiability of a formula, or whether a goal follows from assumptions) expressed in the standard TPTP format.
The usual scenario is a decision problem in first-order logic, but TPTP includes support for higher-order terms (THF format) and for expressing proofs in a standard language (TSTP).

<idea of separate reasoning tools communicating and enhancing a proof development environment>
Evidential tool bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb}.
Omega.
MathServe?
<This is a natural extension of the integration of automatic tools into interactive systems.>
